\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip Estimating \emph{Mycobacterium} tuberculosis transmission in a South African clinic: Spatiotemporal model based on person movements}

### 2024-12-09 doc/paper/supplements.tex
Updates from Overleaf

Particles with \emph{Mtb} in the size range of $1-7\mu$m\cite{Fennelly2020Lancet} have a settling velocity of $3.5\cdot 10^{-5}-1.5\cdot 10^{-3}$m\,s$^{-1}$ in still air\cite{Vuorinen2020SafSci}. Accordingly, we model the settling velocity using a Gamma distribution with mean $7.7\cdot 10^{-3}$m\,s$^{-1}$ and standard deviation $3.7\cdot 10^{-3}$m\,s$^{-1}$, which is slightly skewed towards slower settling velocities, reflecting a higher proportion of \emph{Mtb} at the lower end of the size range\cite{Fennelly2020Lancet}. Assuming a drop height of 1.7\,m, the distribution for the gravitational settling rate has a median of 1.5 h$^{-1}$ (95\%-CrI 0.5 h$^{-1}$ – 3.5 h$^{-1}$).

>>>>

Particles with \emph{Mtb} in the size range of $1-7\mu$m\cite{Fennelly2020Lancet} have a settling velocity of $3.5\cdot 10^{-5}-1.5\cdot 10^{-3}$m\,s$^{-1}$ in still air\cite{Vuorinen2020SafSci}. Accordingly, we model the settling velocity using a Gamma distribution with mean $7.7\cdot 10^{-4}$m\,s$^{-1}$ and standard deviation $3.7\cdot 10^{-4}$m\,s$^{-1}$, which is slightly skewed towards slower settling velocities, reflecting a higher proportion of \emph{Mtb} at the lower end of the size range\cite{Fennelly2020Lancet}. Assuming a drop height of 1.7\,m, the distribution for the gravitational settling rate has a median of 1.5 h$^{-1}$ (95\%-CrI 0.5 h$^{-1}$ – 3.5 h$^{-1}$).
